Evaluating Variable Importances

### 2019-03-28 Scripts/evaluating_model_performances.Rmd
edits to scripts

@@

ggarrange(p25, p25.2, p50, p50.2, p100, p100.2, 
          ncol=2, nrow=3, 
          common.legend = TRUE, 
          legend = "bottom", 
          labels = c("A", "D", "B", "E", "C", "F"), 
          font.label = list(size=20))
```

>>>>

##Plots

@@

figure <- ggarrange(p1,p2,ncol = 2, nrow = 1, common.legend = TRUE, legend = "top")
figure
annotate_figure(figure,
    bottom = text_grob("Resampling Technique", color = "black", size = 20),
    left = text_grob("Performance", color = "black", rot = 90, size=20)
)

figure <- ggarrange(p25, p25.2, p50, p50.2, p100, p100.2, 
          ncol=2, nrow=3, 
          common.legend = TRUE, 
          legend = "top", 
          labels = c("A", "D", "B", "E", "C", "F"), 
          font.label = list(size=20))
figure
annotate_figure(figure,
    bottom = text_grob("Resampling Technique", color = "black", size = 20),
    left = text_grob("Performance", color = "black", rot = 90, size=20)
)

### 2019-03-28 Scripts/evaluating_models_with_dist_preds.Rmd
edits to scripts

```{r}
ggarrange(p.none, p.ros, p.rus, 
          ncol=1, nrow=3, 
          common.legend = TRUE, 
          legend="bottom",
          labels="AUTO",
          font.label = list(size=20))
```

>>>>

```{r}
figure <- ggarrange(p.none, p.ros, p.rus, 
          ncol=1, nrow=3, 
          common.legend = TRUE, 
          legend="top",
          labels="AUTO",
          font.label = list(size=20))
figure
annotate_figure(figure,
    bottom = text_grob("Resampling Technique", color = "black", size = 20),
    left = text_grob("Performance", color = "black", rot = 90, size=20)
)

### 2019-03-28 Scripts/evaluating_variable_importances.Rmd
edits to scripts

```{r}
#GM12878
rfimpvars_gm12878_100kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[1:10,]
#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[10:1,]
rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[1:20,]
rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[20:1,]

@@

vim.gm12878.smote <- vim.gm12878.smote[order(vim.gm12878.smote[,1], decreasing = TRUE),]

@@

vim.K562.smote <- vim.K562.smote[order(vim.K562.smote[,1], decreasing = TRUE),]

@@

vim.gm12878.RUS <- vim.gm12878.RUS[order(vim.gm12878.RUS[,1], decreasing = TRUE),]

@@

vim.K562.RUS <- vim.K562.RUS[order(vim.K562.RUS[,1], decreasing = TRUE),]

@@

vim.gm12878.ROS <- vim.gm12878.ROS[order(vim.gm12878.ROS[,1], decreasing = TRUE),]

@@

vim.K562.ROS <- vim.K562.ROS[order(vim.K562.ROS[,1], decreasing = TRUE),]

@@

vim.gm12878.none <- vim.gm12878.none[order(vim.gm12878.none[,1], decreasing = TRUE),]

@@

vim.K562.none <- vim.K562.none[order(vim.K562.none[,1], decreasing = TRUE),]

@@

>>>>

```{r}
#GM12878
rfimpvars_gm12878_100kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/ENET/RF/rfimpvars.rds")
#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[1:10,]
#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[10:1,]
rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[1:20,]
rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[20:1,]
#rfimpvars_gm12878_100kb_none <- rfimpvars_gm12878_100kb_none[19:1,]

@@

vim.gm12878.smote <- vim.gm12878.smote[order(vim.gm12878.smote[,1], decreasing = TRUE),]
rownames(vim.gm12878.smote) <- gsub("`","",rownames(vim.gm12878.smote))

@@

vim.K562.smote <- vim.K562.smote[order(vim.K562.smote[,1], decreasing = TRUE),]
rownames(vim.K562.smote) <- gsub("`","",rownames(vim.K562.smote))

@@

vim.gm12878.RUS <- vim.gm12878.RUS[order(vim.gm12878.RUS[,1], decreasing = TRUE),]
rownames(vim.gm12878.RUS) <- gsub("`","",rownames(vim.gm12878.RUS))

@@

vim.K562.RUS <- vim.K562.RUS[order(vim.K562.RUS[,1], decreasing = TRUE),]
rownames(vim.K562.RUS) <- gsub("`","",rownames(vim.K562.RUS))

@@

vim.gm12878.ROS <- vim.gm12878.ROS[order(vim.gm12878.ROS[,1], decreasing = TRUE),]
rownames(vim.gm12878.ROS) <- gsub("`","",rownames(vim.gm12878.ROS))

@@

vim.K562.ROS <- vim.K562.ROS[order(vim.K562.ROS[,1], decreasing = TRUE),]
rownames(vim.K562.ROS) <- gsub("`","",rownames(vim.K562.ROS))

@@

vim.gm12878.none <- vim.gm12878.none[order(vim.gm12878.none[,1], decreasing = TRUE),]
rownames(vim.gm12878.none) <- gsub("`","",rownames(vim.gm12878.none))

@@

vim.K562.none <- vim.K562.none[order(vim.K562.none[,1], decreasing = TRUE),]
rownames(vim.K562.none) <- gsub("`","",rownames(vim.K562.none))

@@

##Plots

```{r}
figure <- ggarrange(p1,p2,ncol=2,nrow=1,common.legend = TRUE, legend = "right", labels="AUTO")
figure
annotate_figure(figure,
    bottom = text_grob("Resolution", color = "black", size = 20),
    left = text_grob("Genomic Annotation", color = "black", rot = 90, size=20)
)

figure <- ggarrange(p3,p4,ncol=2,nrow=1,common.legend = TRUE, legend = "right", labels="AUTO")
figure
annotate_figure(figure,
    bottom = text_grob("Resolution", color = "black", size = 20),
    left = text_grob("Genomic Annotation", color = "black", rot = 90, size=20)
)

figure <- ggarrange(p5,p6,ncol=2,nrow=1,common.legend = TRUE, legend = "right", labels="AUTO")
figure
annotate_figure(figure,
    bottom = text_grob("Resolution", color = "black", size = 20),
    left = text_grob("Genomic Annotation", color = "black", rot = 90, size=20)
)

figure <- ggarrange(p7,p8,ncol=2,nrow=1,common.legend = TRUE, legend = "right", labels="AUTO")
figure
annotate_figure(figure,
    bottom = text_grob("Resolution", color = "black", size = 20),
    left = text_grob("Genomic Annotation", color = "black", rot = 90, size=20)
)
